Application of a Cut-Cell Immersed Boundary Method for Wildfire Simulation over Complex Terrain

### 2020-06-10 Vanella_Article_Atmosphere_2020.tex
edits to section 4

>>>>

\subsection{Particle Method}

Lagrangian particles can be used to represent different types of vegetation, like leaves, grass, and so on. In practice each type of vegetation is represented by a single particle in each computational grid cell. Most often the particle is assumed to be cylindrical in shape. The particle is assigned a diameter based on the measured surface area to volume ratio, $\sigma$. The length is relatively unimportant so long as it is assumed to be much greater than the diameter. Material properties are assigned for the wet vegetation which is assumed to dry, decompose to char, and then exothermally oxidize when exposed to heat from an oncoming fire. The drag force exerted by the collection of particles is given by:
\begin{equation}
   \mathbf{f}_{\rm b} = \frac{\rho}{2} \, C_{\rm d} \, C_{\rm s} \, \beta \, \sigma \, \mathbf{u} \, ||\mathbf{u}||
\end{equation}
where $\rho$ is the air density, $C_{\rm d}$ is the drag coefficient, $C_{\rm s}$ is the shape factor (ratio of projected area to surface area), $\beta$ is the packing ratio, $\sigma$ is the surface area to volume ratio, and $\mathbf{u}$ is the air velocity. The diameter is specified via the surface area to volume ratio, $\sigma=2/r$ for a cylinder. The packing ratio is the volume of solid needles divided by the volume they occupy, typically denoted $\beta$. It is calculated by dividing the dry mass of vegetation per unit volume, the so-called ``bulk density,'' by the density of the dry vegetation, $\rho_{\rm d}$.

A coniferous tree (e.g. pine, spruce, fir) can be represented in FDS as a collection of Lagrangian particles forming a large cone. The trunk and heavier branches are typically neglected.
